An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-29 VLDB2026/main.tex
Update main.tex
modify

	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some algorithms, it presents several notable limitations:
	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. 2) It \sout{focuses only on single-attribute and dual-attribute query scenarios,} neglecting the more complex demands of multi-attribute queries. In real-world applications, an object typically involves multiple attributes. For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.
	3) It does not evaluate algorithm performance under different attribute distributions. However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.

@@

	(5)\textbf{ Recommendations and Challenges.}
	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries. These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution. \sout {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}

@@

	\noindent\textbf{\underline{UNG \cite{UNG}.}} The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low. UNG is proposed to overcome these limitations.
	UNG is a unified framework that integrates diverse graph-based ANN indexes for hybrid query. It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes. Then, it constructs a Label Navigating Graph (LNG) to encode inclusion relationships among attribute sets. Within each group, UNG builds graph-based ANN indexes (e.g., Vamana, HNSW) and connects them via cross-group edges to enable efficient cross-group search.
	%UNG supports Boolean filtering with 2 modes:  1) The query attribute set is a subset of the data attribute set.  2) The query attribute set exactly matches the data attribute set.

@@

		\footnotesize{
			\begin{minipage}{\linewidth}
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport.
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
			\end{minipage}

>>>>

	Despite BigANN 2023 \cite{bigann2023} evaluates the performance of some algorithms, it presents several notable limitations:
	1) The evaluation covers a limited number of algorithms and fails to comprehensively include mainstream methods. 
	\sout{For instance, attribute filtering algorithms such as NHQ and UNG are not included in the evaluation. }
	2) It \textcolor{blue}{focuses only on single-attribute and dual-attribute query scenarios,} 
	\sout{neglecting the more complex demands of multi-attribute queries. In real-world applications, an object typically involves multiple attributes.}\textcolor{blue}{ \sout{For example, in e-commerce scenarios, users often specify multiple attributes (e.g., color, brand, price range) simultaneously when searching.}}
	3) It does not evaluate algorithm performance under different attribute distributions. 
	\sout{However, variations in attribute distribution may directly affect the filtering strategies and index construction efficiency of hybrid query algorithms.}

@@

	(5)\textbf{ Recommendations and Challenges.}
	Based on the experimental results, we provide algorithm selection recommendations for common application scenarios and highlight key challenges in the field of hybrid queries. These challenges include limited Boolean logic support, the lack of multi-attribute range filtering capabilities, and the sensitivity of algorithms to data distribution. \textcolor{blue} {Currently, few methods simultaneously support both attribute filtering and range filtering, pointing to potential directions for future research.}

@@

	\noindent\textbf{\underline{UNG \cite{UNG}.}} 
	\sout{The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low. UNG is proposed to overcome these limitations.}
	UNG is a unified framework that integrates diverse graph-based ANN indexes for hybrid query. It first groups the dataset by attribute sets, ensuring that vectors in each group share identical attributes. Then, it constructs a Label Navigating Graph (LNG) to encode inclusion relationships among attribute sets. Within each group, UNG builds graph-based ANN indexes (e.g., Vamana, HNSW) and connects them via cross-group edges to enable efficient cross-group search.
	%UNG supports Boolean filtering with 2 modes:  1) The query attribute set is a subset of the data attribute set.  2) The query attribute set exactly matches the data attribute set.

@@

		\footnotesize{
			\begin{minipage}{\linewidth}
				\centering
				The indicators are consistent with those in Table ~\ref{tab:compair_1}.
%				\textsuperscript{Y} Support, 
%				\textsuperscript{N} Unsupport.
%				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
%				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
%				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
			\end{minipage}
